|

### 2019-03-21 rap/article.Rmd
update types

The Report distinguishes between different types of violence carried out by the Pinochet regime. The first type is _deaths_. These are cases where the Commission signals a definite and known death of the victim. Take the case of Benito Heriberto Torres Torres, one of the first victims of the Pinochet regime (id number 2). Our dataset shows that Mr Torres was male, 57 years-old, and that he worked as a plumber. On the 12 September 1973, just one day after the military coup, Mr Torres was torture on the way to the 26th police station in Santiago. The records indicate he executed and his body was later found in Las Barrancas, Santiago. The dataset also shows that we obtained this information from pages 159-160 in the Truth Commission Report.

@@

The third category refers to _disappearance, information of death_. As the name implies,

the Commission has information

 that signals that "the victims are dead; that they died at the hands of the government agents, or persons in their service; and that these or other agents disposed of the victims' mortal remains by throwing them into a river or a sea, by covertly burying them, or by disposing of them in some other secret fashion" [-@report1991 44]. _Unresolved_ cases are those where insufficient information or evidence is available.

From the report, we identify 1,331 murders, 853 disappearances, 108 cases of disappearances where some information about the victim was available, 93 unresolved cases, and 7 suicides[^ambiguous]. However, it is very likely that the people who disappeared were, in fact, killed. Based on the report and our methodology, we can only determine that 65% of all of the cases led to an assassination. Forty percent of the documented cases are disappearances.

>>>>

The Report distinguishes between different types of violence carried out by the Pinochet regime. The first type is _deaths_. These are cases where the Commission signals a definite and known death of the victim. Take the case of Benito Heriberto Torres Torres, one of the first victims of the Pinochet regime (id number 2). Our dataset shows that Mr Torres was male, 57 years-old, and that he worked as a plumber. On the 12 September 1973, just one day after the military coup, Mr Torres was torture on the way to the 26th police station in Santiago. The records indicate he executed and his body was later found in Las Barrancas, Santiago. The dataset also shows that we obtained this information from pages 159-160 of the Truth Commission Report.

@@

The third category is _disappearance, information of death_. As the name implies, these observations refer to cases the Commission confirms the individual died after being missing. The formal definition for this category is that "the victims are dead; that they died at the hands of the government agents, or persons in their service; and that these or other agents disposed of the victims' mortal remains by throwing them into a river or a sea, by covertly burying them, or by disposing of them in some other secret fashion" [-@report1991 44]. The assassination of Humberto de las Nieves Fuentes Rodriguez is an example (id number 854). He was taken in custody to the Colina air base, then loaded onto a helicopter with other political prisoners. According to the Report, government agents drugged him, beat him with a metal bar, opened his stomach with a knife before throwing the former Communist alderman from a helicopter. While his body has not been found, there is enough information about the case to classify his death as a severe human rights violation.

The last group is that of _unresolved_ cases. These are defined as those where insufficient information or evidence is available. Our dataset counts 93 unresolved cases, many with georeferenced information about possible torture sites[^ambiguous]. However, it is very likely that the people who disappeared were, in fact, killed. Based on the report and our methodology, we can only determine that 65% of all of the cases led to an assassination. Forty percent of the documented cases are disappearances.
